Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-06 paper/abstract_aas.tex
add abstract for AAS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\newcommand{\tn}{TOI~837} % target star name
\newcommand{\pn}{TOI~837b} % planet name
\newcommand{\cn}{IC~2602} % cluster name

\newcommand{\kms}{\,km\,s$^{-1}$}

\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
\newcommand{\datasetlink}{\textsc{\dataset[doi.org/10.17909/t9-ayd0-k727]{https://doi.org/10.17909/t9-ayd0-k727}}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

\begin{document}

\defcitealias{bouma_wasp4b_2019}{B19}

\title{
  Cluster Difference Imaging Photometric Survey. II.
  TOI~837: A Young Validated Planet in IC~2602
}

%\suppressAffiliations
%\NewPageAfterKeywords
\input{authors.tex}

\begin{abstract}
  We report the discovery of TOI 837b and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
  southern open cluster IC 2602.  The star and planet are therefore
  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the planet has an orbital
  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial
  velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
  $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly
  graze the stellar limb.  Grazing transits are a cause for concern,
  as they are often indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is
  therefore a validated adolescent exoplanet.  The planetary nature of
  the system can be confirmed or refuted through observations of the
  stellar obliquity and the planetary mass.  Such observations may also
  improve our understanding of how the physical and orbital properties
  of exoplanets change in time.
\end{abstract}

\keywords{
	Exoplanets (498),
  Transits (1711),
	Exoplanet evolution (491),
	Stellar ages (1581),
	Young star clusters (1833)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Over the first 100 million years of their lives, exoplanet systems are
expected to undergo major physical and dynamical changes.  For a
typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,fedele_timescale_2010,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the end of disk
dispersal \citep{pollack_formation_1996}.  While rocky planets may
form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
over the next 10--100 million years through giant impacts \citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal during Earth's
first 100 million years
\citep{cameron_origin_1976,canup_origin_2001,touboul_late_2007}.

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
Predicted timescales for photoevaporation and core-powered mass loss
range from 10 million years to over 1 gigayear for typical transiting
sub-Neptunes
\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
The relative importance of each process is set by the planetary
surface gravity and the radiation environment.  Both processes can be
directly observed through observations of planetary winds in the
metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
The circularization timescale is thought to be such that for any giant
planets that migrated early, their orbits should circularize within
100 million years \citep{zahn_tidal_1977}.

Finding and understanding systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting
V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
not confirm the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

The transit method was comparatively slow to catch up.  Early deep
transit searches of open clusters by many groups did not yield
definitive planet detections
\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006,aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008,pepper_photometric_2008,hartman_MMT_IV_2009}.
These searches were typically sensitive to planets larger than
Jupiter, on $\lesssim 3$ day orbital periods.  Hot Jupiter occurrence
rate limits were derived at the $\lesssim 5\%$ level \citep[{\it
e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
occurrence rate suggests that these early transit surveys would have
needed a greater data volume at higher precision for detection to be
possible
\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.

Kepler observed a large enough number of stars with sufficient
baseline and precision to detect transiting planets in open clusters:
Kepler-66b and 67b, in the gigayear-old NGC~6811
\citep{borucki_kepler_2010,Meibom_et_al_2013}.  Though a broken
reaction wheel ended the prime Kepler mission, the repurposed K2
\citep{howell_k2_2014} switched between fields along the ecliptic
every quarter-year, and was able to observe far more clusters and
young stars.

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets in clusters may in fact be qualitatively
different from their field counterparts.  For instance, based on its
observed mass, radius, and UV environment, the 700$\,$Myr K2-100b is
probably actively losing its atmosphere, and should become a bare
rocky planet over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets around V1298~Tau (23$\,$Myr) are also likely to be
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

To advance the young planet census, we have been using data from the
TESS spacecraft \citep{ricker_transiting_2015} to perform a Cluster
Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink}, and through \datasetlink.  Searching
through a subset of these light curves brought our attention to the
candidate transiting planet, \pn, that is the subject of this
analysis.

The transits of \pn\ are grazing the stellar limb, which is a cause
for concern.  Particularly for a star near the galactic plane
($b=-5.8^\circ$), background eclipsing binaries are a major source of
astrophysical false positives \citep[{\it
e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
and related scenarios are unlikely to the degree that we can
validate the planet, {\it i.e.}, determine that its probability of
being an astrophysical false positive is small.  We
considered this result worth reporting because of the planet's youth.

Section~\ref{sec:observations} describes the identification of the
candidate, and our follow-up observations.
Section~\ref{sec:validation} combines the available data to assess the
system's false positive probability, and validates \pn\ as a planet.
Section~\ref{sec:system} presents our knowledge of the cluster
(Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
and the planet (Section~\ref{subsec:planet}).  We conclude by
discussing avenues for confirmation and improved characterization in
Section~\ref{sec:discussion}.

\section{Identification and Follow-up Observations}
\label{sec:observations}

\subsection{TESS Photometry}
\label{subsec:tess}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.79\textwidth]{f1a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are
    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
    transit.  Gray points are 2-minute measurements with the local
    spot-induced variation removed.  Binning at 6-minute intervals
    yields the black points.  The black error-bar shows the median
    uncertainty for the black points.  The gray line shows the
    best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
the tenth and eleventh sectors of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
$11\times11$ array surrounding the star were co-added and saved at
2-minute cadence.  The $2048\times2048$ image from the entire CCD was
also co-added into 30-minute stacks, and saved as a ``full frame
image'' (FFI).

The TESS Science Processing Operations Center
\citep{jenkins_tess_2016} processed the image data and identified the
transiting planet signature from two transits in
Sector 10, again with three transits in Sector 11, and then for a
final time when Sectors 1-13 were searched at the end of the first
year of the mission. The transit signature was fitted with a
limb-darkened transit model \citep{li_kepler_2019} and passed all the
diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
depth test, the weak secondary eclipse test, the ghost diagnostic
test, and the difference image centroiding test, which placed the
transit source within $\sim$2 arcsec of the location of TOI~837. No
additional transit-like features were identified in any of the SPOC
searches. The TESS Science Office alerted the community to this
candidate transiting planet on 17 June 2019.  Our subsequent blind
search of the CDIPS FFI light curves also showed the transits. Given
that the 2-minute data had better sampling cadence, we opted to use
the Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips are
suggestive of a grazing transiting planet, recurring roughly every 8
days with a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models shown in these plots is described in
Section~\ref{subsec:planet}.

\subsection{Gaia Astrometry and Imaging}
\label{subsec:gaia}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10, with a logarithmic
    grayscale. The yellow star is the position of \tn.  White circles
    are resolved Gaia sources with $T<16$. Brighter stars are larger.
    The black \texttt{X} and white \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible
    sources of the transits.
		\label{fig:scene}
	}
\end{figure}

Between 25 July 2014 and 23 May 2016, the ESA Gaia satellite measured
about 300 billion centroid positions of 1{.}6 billion stars.  The
positions, proper motions, and parallaxes of the brightest 1{.}3
billion were calculated for the second data release (DR2)
\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
\tn\ was assigned the Gaia DR2 identifier 5251470948229949568, and had
276 ``good'' astrometric observations. Its brightness was measured in
the $G$, $Rp$, and $Bp$ bands of the Radial Velocity Spectrometer
\citep{cropper_gaia_2018,evans_gaia_2018}.

The Gaia imaging, reduced to its point-source catalog, provides the
initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
Given its galactic latitude of $b=-6^\circ$, it is not surprising that
the field of \tn\ is crowded.  The resolved stars that were of
immediate concern for our false positive analysis were as follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
    proper motions and parallax of this star imply it is co-moving
    with \tn\ and that the two stars are separated by $6.6\pm
    0.1\,{\rm pc}$.  Star A is therefore likely an \cn\ member, but
    unlikely to be a bound binary companion.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
    Gaia parallax implies this is a background giant star.
\end{itemize}
An additional source, TIC 847769581, is $4.9''$ from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412},
\texttt{2020-07-08}. } value is available.  We suspect that the
photometric failure to produce an $Rp$ magnitude as well as its poor
astrometric fit are due to blending with \tn.

At the $\approx1'$ resolution of the TESS data, if either Star A or
Star B were eclipsing binaries, they could be the sources of the
transit signal.  A detailed analysis of ground-based seeing-limited
photometry was necessary to assess and rule out this possibility
(Section~\ref{subsec:groundphot} and Figure~\ref{fig:groundphot}).

\subsection{High-Resolution Imaging}
\label{subsec:speckle}

To determine if any fainter point sources existed closer to \tn\
inside of Gaia's point-source detection limits, we acquired
high-resolution speckle images. We then searched the autocorrelation
functions of these images for peaks indicative of nearby companions.

The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:speckle}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.  Star B was not detected; with a separation of $5.4''$ from
\tn, it fell outside the field of view.

\subsection{Ground-based Time-Series Photometric Follow-up}
\label{subsec:groundphot}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescop at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

We obtained ground-based seeing-limited time series photometric
observations of \tn\ bracketed around the times of transit.  These
observations confirmed that the transits occurred on-target to within
$\approx 2''$, and that they were achromatic. Both features are
essential for our ability to eliminate false-positive scenarios.

\subsubsection{El Sauce 0.36$\,$m}

\paragraph{Acquisition and reduction}
We observed four transits with the 0.36$\,$m telescope at Observatorio
El Sauce, located in the R\'io Hurtado Valley in Chile, and operated
by co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

We scheduled our transit observations using the {\tt TESS Transit
Finder}, which is a customized version of the {\tt Tapir} software
package \citep{Jensen:2013}.  The photometric data were calibrated and
extracted using \texttt{AstroImageJ} \citep{collins_astroimagej_2017}.
Comparison stars of similar brightness were used to produce the final
light curves, each of which showed a roughly 4$\,$ppt dip near the
expected transit time.  The data are reported in Table~\ref{tab:phot}
and plotted in Figure~\ref{fig:groundphot}.

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  The typical FWHM for
stars in the El Sauce observations was $\approx 2.3''$, with a
variance of $\approx 0.2''$.  Star B is resolved in the 0.36$\,$m
images; Star A is not.

To rule out blend scenarios with the ground-based photometry, we
produced light curves centered on \tn\ with circular apertures of
radii ranging from 0.7$''$ to 5.1$''$.  We did not detect any
statistically significant variation in the depth of the transits with
aperture size.  Two lines of evidence rule out Star B as the eclipsing
source: first, the transits were detected in the smallest apertures.
Second, we made light curves with $2.1''$ apertures centered on Star
B, and they did not show the transit.

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ West of \tn) to
2.3$''$ East of \tn.  We did not detect any variation of the transit
depth along this line of light curves. The apertures East of \tn\
exclude over 90\% of the flux from Star A.  The eclipse on Star A
would therefore need to have depth greater than unity to produce the
observed eclipse depth.  We therefore interpret the lack of asymmetry
between the Western-most (centered on Star A) and Eastern-most
(furthest from Star A) light curves as conclusive evidence that \tn\
is the source of the transit signal to within $\approx2.0''$.  To
verify self-consistency, we checked that the maximum dilution from
Star A ($\approx 1\%$) is less than the uncertainty of the transit
depth measurements ($\approx 15\%$), and so the lack of variation of
transit depth with aperture location is consistent with \tn\ being the
source of transits.

\subsubsection{ASTEP400}

We observed three transits with the 0.40$\,$m ASTEP telescope at the
Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
Concordia base is operated by the French and Italian polar
institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
allows it to take advantage of the continuous night during Austral
winter.  The weather is of photometric quality for about two-thirds of
each winter \citep{crouzet_four_2018}.

ASTEP is equipped with a FLI Proline science camera with a KAF-16801E,
$4096\times4096$ front-illuminated CCD. The camera has an image scale
of 0.93\,arcsec pixel$^{-1}$ resulting in a $1^{\circ}\times1^{\circ}$
corrected field of view. The focal instrument dichroic plate splits
the beam into a blue wavelength channel for guiding, and a
non-filtered red science channel roughly matching a Cousins-R
transmission curve
\citep{abe_secondary_2013,mekarnia_transiting_2016}.  The images were
processed on-site using an automated aperture  photometry pipeline
based on the \texttt{daophot} package of the IDL astronomy user's
library \citep{landsman_1995}.

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processing overhead of $25\,$s).  Except for
12 May, our observations were conducted under stable weather
conditions, with clear skies, temperatures of about $-70^\circ$C, and
wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
exclude from the analysis all data collected on May 12. We found that
the optimal calibrated light curves of \tn\ correspond to an 11 pixel
(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
observations carried out on June and May, respectively.  The data are
reported in Table~\ref{tab:phot}, and plotted in
Figure~\ref{fig:groundphot}.

\input{TOI837_phot_table.tex}

\subsection{Spectroscopic Follow-up}
\label{subsec:spectra}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.44\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
    imaging were derived from point-source injection-recovery
    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
    \label{fig:speckle}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.47\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

Reconnaissance spectroscopic follow-up is an essential step in vetting
planet candidates.  Medium to high-resolution spectra enable physical
characterization of the star and therefore planet.  Reducing multiple
spectra to a radial velocity time-series can enable planet mass
measurements, and also set limits on the mass of any nearby
companions.  Finally, if there are close or bright companions,
reconnaissance spectra can also reveal the presence of a secondary set
of stellar lines.

\subsubsection{SMARTS 1.5$\,$m / CHIRON}
\label{subsec:chiron}

We acquired nine spectra using CHIRON at the SMARTS 1.5$\,$m telescope
at Cerro Tollo Inter-American Observatory, Chile
\citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
requirements for radial velocity measurements and stellar parameter
extraction.  We used CHIRON in its image slicer configuration,
yielding a spectral resolution of $\approx 79{,}000$ across
415--880$\,$nm.

We derived radial velocities and spectroscopic line profiles from the
CHIRON observations using a least-squares deconvolution of the spectra
against non-rotating synthetic spectral templates
\citep{donati_1997_spectropolarimetric}. The spectral templates were
generated using ATLAS9 atmosphere models \citep{Castelli:2004} with
the \texttt{SPECTRUM} script \citep{gray_1994_spectrum}. These line
profiles were fitted with a broadening kernel that describes the
rotational, radial-tangential macroturbulent, and instrumental
broadening of the spectrum. The rotational and macroturbulent
broadening are computed per \citet{gray_2005_book}, following the
methods described in \citet{zhou_2018_hd106315obliq}. We fitted the
line profile from each observation independently, yielding the radial
velocities listed in Table~\ref{tab:rvs} and shown in
Figure~\ref{fig:rvs}. We found a mean rotational broadening velocity
of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
macroturbulent broadening of $v_\mathrm{mac} = 8.4 \pm 2.9
\mathrm{km\,s}^{-1}$.

To derive the stellar parameters, we matched the set of CHIRON spectra
against a library of observed spectra, previously obtained using the
Tillinghast Reflect Echelle Spectrograph
\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
Lawrence Whipple Observatory (FLWO), Arizona, USA, and classified
using the Stellar Parameter Classification pipeline
\citep{buchhave_hatp16b_class_2010}.  We found the best matching
stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} = -0.069 \pm 0.042$ dex.
We ultimately adopted a different set of stellar parameters for our
analysis (see Section~\ref{subsec:starparams}).

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines was found. To set limits on the contributions of a close-by
star to the observed spectrum, we injected a second set of lines to
the mean least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$. The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.

\subsubsection{FEROS}
TOI 837b was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
telescope at the ESO La Silla Observatory, in Chile. FEROS has a
resolution of $\approx$48,000 across a spectral range of 350–920 nm.
It has a high efficiency of $\approx$20\%. We obtained 13
spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
context of the Warm gIaNts with tEss (WINE) collaboration, which
focuses on the systematic characterization of TESS transiting giant
planets with moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
shown in Figure~\ref{fig:rvs}.  To check for the presence of secondary
lines, we performed a similar injection-recovery exercise as with the
CHIRON data.  We achieved slightly worse limits, likely due to the
lower spectral resolution of FEROS, and therefore adopted the CHIRON
limits.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the 3.9$\,$m Anglo-Australian Telescope at
Siding Spring Observatory near Coonabarabran, Australia
\citep{gilbert_veloce_2018}.  The currently operational
``Veloce-Rosso'' channel provides coverage from 600--950$\,$nm at a
spectral resolution of $\approx 80{,}000$.  Many of the exposures were
taken in average or poor seeing conditions, when the SNR is lowest and
the fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a template of $\delta$ Pavonis, because with spectral type G8
IV it was the closest high-SNR \tn\ analog available in the Veloce
spectral database.  The velocity RMS seen across each visit was
hundreds of meters per second, likely due to uncorrected
fiber-to-fiber cross-contamination.  This cross-contamination severely
affects the wavelength solutions for the 19 individual science fibres,
ultimately leading to significantly increased RV scatter. For analysis
purposes, we averaged the single-shot RVs across each visit, and set
the velocity uncertainties to be the standard deviation of the
per-visit exposures.  The velocities are given in Table~\ref{tab:rvs},
and shown in Figure~\ref{fig:rvs}.

\input{TOI837_rv_table.tex}

\section{Assessment of False Positive Scenarios}
\label{sec:validation}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.75\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
    companions along the same line of sight (BEB scenarios).  Each
    constraint is described in Section~\ref{subsec:fp_constraints}.
    Gray regions are ruled out by at least one constraint.
		\label{fig:fpscenario}
	}
\end{figure*}

>>>>

We report the discovery of TOI 837b and its validation as a transiting planet.  We characterize the system using data from the NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the southern open cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$ million years old.  Combining the transit photometry with a prior on the stellar parameters derived from the cluster color-magnitude diagram, we find that the planet has an orbital period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly graze the stellar limb.  Grazing transits are a cause for concern, as they are often indicative of astrophysical false positive scenarios.  Our follow-up data show that such scenarios are unlikely.  Our combined multi-color photometry, high-resolution imaging, and radial velocities rule out hierarchical eclipsing binary scenarios.  Background eclipsing binary scenarios, though limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is therefore a validated adolescent exoplanet.  The planetary nature of the system can be confirmed or refuted through observations of the stellar obliquity and the planetary mass.  Such observations may also improve our understanding of how the physical and orbital properties of exoplanets change in time.
